The Bot on Speaking Terms: The Effects of Conversation Architecture on Perceptions of Conversational Agents

### 2023-06-06 paper.tex
submitted version to CUI 2023
finalized copy uploaded to TAPS

%% Manuscript for the effect of designed conversational architecture on the perception of agents
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,screen,review, anonymous]{config/acmart}

\usepackage[linewidth=1pt]{mdframed}
\usepackage{lipsum}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{makecell}

@@

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2023}
\acmYear{2023}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation email}{June 03--05,
  2018}{Woodstock, NY}
%
%  Uncomment \acmBooktitle if th title of the proceedings is different
%  from ``Proceedings of ...''!
%
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%  June 03--05, 2018, Woodstock, NY} 
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Conversational agents mimic natural conversation to interact with users. Since the effectiveness of interactions strongly depends on users’ perception of agents, it is crucial to design agents’ behaviors to provide the intended user perceptions. Research on human-agent and human-human communication suggests that speech specifics are associated with perceptions of communicating parties, but there is a lack of systematic understanding of how speech specifics of agents affect users' perceptions. To address this gap, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness). Synthesized based on literature reviewed from the domains of HCI, NLP and linguistics (n=57), this framework demonstrates both the identified relationships and the areas lacking empirical evidence. We discuss the implications of the framework for conversation design and highlight the inconsistencies with terminology and measurements.
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{conversational agents, user perception, conversation architecture, anthropomorphized perceptions}

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
TBD
\end{acks}

@@

>>>>

%% Manuscript for the effect of designed conversational architecture on the perception of agents
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,screen]{config/acmart}

%\usepackage[linewidth=1pt]{mdframed}
\usepackage{lipsum}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{makecell} 
\usepackage{stfloats}
\usepackage{longtable}

@@

\usepackage{soul}
\usepackage{color}
\newcommand{\hlrev}[1]{{\sethlcolor{yellow}\hl{#1}}}

@@

\copyrightyear{2023} 
\acmYear{2023} 
\setcopyright{acmlicensed}\acmConference[CUI '23]{ACM conference on Conversational User Interfaces}{July 19--21, 2023}{Eindhoven, Netherlands}
\acmBooktitle{ACM conference on Conversational User Interfaces (CUI '23), July 19--21, 2023, Eindhoven, Netherlands}
\acmPrice{15.00}
\acmDOI{10.1145/3571884.3597139}
\acmISBN{979-8-4007-0014-9/23/07}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%\setcopyright{acmcopyright}
%\copyrightyear{2023}
%\acmYear{2023}
%\acmDOI{3571884.3597139}

%% These commands are for a PROCEEDINGS abstract or paper.
%\acmConference[Conference acronym 'XX]{Make sure to enter the correct
%  conference title from your rights confirmation email}{June 03--05,
%  2018}{Woodstock, NY}
%
%  Uncomment \acmBooktitle if th title of the proceedings is different
%  from ``Proceedings of ...''!
%
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%  June 03--05, 2018, Woodstock, NY} 
%\acmPrice{15.00}
%\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.

\begin{abstract}
Conversational agents mimic natural conversation to interact with users. Since the effectiveness of interactions strongly depends on users’ perception of agents, it is crucial to design agents’ behaviors to provide the intended user perceptions. Research on human-agent and human-human communication suggests that speech specifics are associated with perceptions of communicating parties, but there is a lack of systematic understanding of how speech specifics of agents affect users' perceptions. To address this gap, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness). Synthesized based on literature reviewed from the domains of HCI, NLP and linguistics (n=57), this framework demonstrates both the identified relationships and the areas lacking empirical evidence. We discuss the implications of the framework for conversation design and highlight the inconsistencies with terminology and measurements.
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{conversational agents, natural language interface, chatbots, virtual assistants, user perceptions, anthropomorphized perceptions, conversation architecture, speech variations}

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
This work was supported by NAVER Corp.
\end{acks}

@@

\input{sections/7-appendix}

### 2023-06-06 sections/1-introduction.tex
finalized copy uploaded to TAPS

Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities. Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions with users \cite{knijnenburg2016inferring, seeger2021chatbots}, i.e. supporting users in achieving their goals. For instance, previous research suggests that there is a relationship between CAs' conversation architecture and how users perceive these agents %.
%While various studies investigated how some elements of conversation architecture affect users' perceptions of agents~
(e.g.,~\cite{clark2019state, feine2019taxonomy, finch2020towards}).  However, there is currently a lack of systematic understanding of these relationships, i.e. what elements of conversation architecture are impactful for users' perceptions and how. Specifically, while various studies investigated how some elements of conversation architecture affect aspects of users' perceptions or discussed the speech specifics of agents as part of a broader analysis of the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for 
conversation architecture elements that are relevant to user perceptions. Yet, this systematic understanding is essential for guiding the design of conversation architecture, which would allow us to both predict and develop users' appropriate perceptions of agents.

@@

%These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents 
To address this gap, %in this paper, we
%we aim to understand how to design conversation architecture in order to orchestrate perceptions of conversational agents.
%First, we 
we explore the following research questions in this paper: \textbf{(RQ1) what aspects of users' perceptions of agents have been explored in relation to the effects of conversation architecture elements?}, \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?}, and \textbf{(RQ3) what is known about the specifics of these relationships between conversation architecture elements and the perceptions of CAs?}
%While there are various elements of conversation architecture used in a CA's utterances, we don't have a systematic understanding of them. This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
To answer these questions, we performed a comprehensive review of the existing literature published from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on the final dataset of 57 relevant papers (\autoref{fig:heatmap_identified}). Based on this review, we grouped the perceptions of agents that were shown to be affected by conversation architecture into four categories (interaction, ability, sociability and humanness) and eleven aspects (\autoref{tbl:perceptions}), and grouped the speech variations related to perceptions of agents into four categories (dialog strategy, content affectiveness, content style and speech format) and eleven elements (\autoref{tbl:conversation_architecture}). 
We found that perceptions of interaction with CAs (usability, engagement, satisfaction) have been most explored in relation to speech variations, while the perceptions of CAs' ability (intelligence, competence, credibility) have been explored the least.
%the least number of explored and identified relationships. 
Our results also show that the conversation architecture elements of response delay and agent-initiated dialog related to perceptions of CAs are under-explored in literature. 
Thus, our work contributes to the CUI community by presenting a framework that synthesizes the findings on the effect of conversation architecture on perceptions of conversational agents while also identifying and clustering perception aspects and conversation architecture elements. %, providing clear and consistent terms that can be used in future research. Together, these contributions move us one step closer to designing CAs that effectively interact with users.

>>>>

Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities. Since these agents communicate in natural language, the effectiveness of interactions between users and conversational agents in achieving users' goals depend heavily on the \textit{conversation architecture}, which refers to the content and manner of communication utilized by the agents \mbox{\cite{knijnenburg2016inferring, seeger2021chatbots}}.
%\textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions with users \cite{knijnenburg2016inferring, seeger2021chatbots}, i.e. supporting users in achieving their goals. 
%For instance, p
Previous research suggests that there is a relationship between CAs' conversation architecture and how users perceive these agents %.
%While various studies investigated how some elements of conversation architecture affect users' perceptions of agents~
(e.g.,~\cite{clark2019state, feine2019taxonomy, finch2020towards}).  
%\hlrev{However, there is currently a lack of overall comprehension of the relationship between users' perceptions and conversation architecture elements, specifically which elements are significant and how they impact these perceptions.}
%However, there is currently a lack of systematic understanding of these relationships, i.e. what elements of conversation architecture are impactful for users' perceptions and how they impact these perceptions. 
While various studies investigated how some elements of conversation architecture affect aspects of users' perceptions or discussed the speech specifics of agents as part of a broader analysis of the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for 
conversation architecture elements that are relevant to user perceptions. 
As such, this paper aims to provide a systematic understanding of the effect of conversation architecture elements on users' perceptions of conversational agents. Such an understanding is essential for guiding the design of conversation architecture, which would allow us to both predict and develop users' appropriate perceptions of agents.

@@

%These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents

%To address this gap, %in this paper, we
%we aim to understand how to design conversation architecture in order to orchestrate perceptions of conversational agents.
%First, we 
To gain this systematic understanding, we explored the following research questions in this paper: \textbf{(RQ1) what aspects of users' perceptions of agents have been explored in relation to the effects of conversation architecture elements?}, \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?}, and \textbf{(RQ3) what is known about the specifics of these relationships between conversation architecture elements and the perceptions of CAs?}
%While there are various elements of conversation architecture used in a CA's utterances, we don't have a systematic understanding of them. This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
In order to answer these questions, we performed a comprehensive review of the existing literature published from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on the final dataset of 57 relevant papers (\autoref{fig:heatmap_identified}). Based on this review, we grouped the perceptions of agents that were shown to be affected by conversation architecture into four categories (interaction, ability, sociability and humanness) and eleven aspects (\autoref{tbl:perceptions}), and grouped the speech variations related to perceptions of agents into four categories (dialog strategy, content affectiveness, content style and speech format) and eleven elements (\autoref{tbl:conversation_architecture}). 
We found that perceptions of interaction with CAs (usability, engagement, satisfaction) have been most explored in relation to speech variations, while the perceptions of CAs' ability (intelligence, competence, credibility) have been explored the least.
%the least number of explored and identified relationships. 
Our results also show that the conversation architecture elements of response delay and agent-initiated dialog related to perceptions of CAs are under-explored in literature. 
Thus, our work contributes to the CUI community by presenting a framework that synthesizes the findings on the effect of conversation architecture on perceptions of conversational agents while also identifying and clustering perception aspects and conversation architecture elements. %, providing clear and consistent terms that can be used in future research. Together, these contributions move us one step closer to designing CAs that effectively interact with users.

### 2023-06-06 sections/3-method.tex
finalized copy uploaded to TAPS

\subsection{Data Collection}
To perform a literature analysis of past findings on the relationship between the specifics of conversation architecture and perceptions of CAs, we identified, reviewed, and selected relevant literature using PRISMA guidelines \cite{prisma}. %, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs. 
Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023. Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements or aspects of perceptions. As such, we generalized our search term to capture articles related to conversational agents. Based on search terms used in previously published literature reviews \cite{clark2019state, rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
\newline

@@

\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper. We used inductive thematic analysis to group these assessments into codes based on their meanings. For example, likeability of the agent contains Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]} and questionnaire items like ``\textit{this voice agent was likeable}'' used by \cite{cuadra2021my}\cmt{[67]}. This step resulted in 83 unique codes. These codes are then organized based on similarity of their meanings, resulting in 11 aspects of perceptions. For instance, the aspect of personality traits of the agent contains codes such as likeability, funniness, and kindness. Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (\autoref{tbl:perceptions}).

>>>>

\subsection{Data Collection}
To perform a literature analysis of past findings on the relationship between the specifics of conversation architecture and perceptions of CAs, we identified, reviewed, and selected relevant literature using PRISMA guidelines \cite{prisma}. %, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs. 
In accordance with accepted practices, we defined the scope of our literature review by considering two factors: (1) time---specifically publications from 2010 to 2022---and (2) source---using the ACM Digital Library \mbox{\cite{zheng2022ux, stigall2019older, mcconvey2023human}.}
%Searches were carried out between January 1 and January 15, 2023. 
Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements or aspects of perceptions. As such, we generalized our search term to capture articles related to conversational agents. Based on search terms used in previously published literature reviews \cite{clark2019state, rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
\newline

@@

We analyzed the data by conducting reflexive thematic analysis approach with open and axial coding procedures \mbox{\cite{braun2019reflecting}}. First, we performed open coding on each article to extract labels related to perceptions of agents and conversation architecture. These labels were then grouped into conceptual categories through axial coding. The first author was responsible for performing the data analysis, with the second and third authors cross-checking the codes. We resolved disagreements through regular discussions and multiple rounds of revisions.

\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper. 
%We used inductive thematic analysis to group these assessments into codes based on their meanings. 
For example, likeability of the agent contains Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]} and questionnaire items like ``\textit{this voice agent was likeable}'' used by \cite{cuadra2021my}\cmt{[67]}. This step resulted in 83 unique codes. These codes are then organized based on similarity of their meanings, resulting in 11 aspects of perceptions. For instance, the aspect of personality traits of the agent contains codes such as likeability, funniness, and kindness. Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (\autoref{tbl:perceptions}).

### 2023-06-06 sections/5-discussion.tex
finalized copy uploaded to TAPS

There has been some effort recently towards unifying the evaluation of conversational agents, such as the work by Finch et al. \cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols. More research is needed in this area to standardize the assessment of perceptions to make them consistent, granular, and comparable across literature.

@@

\subsection{Ethical Considerations}

The designers of conversational agents need to consider ethical implications and potential negative impacts for users. This section discusses three main areas of concern related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing users' actions, and privacy concerns.

For the element of prosody, various studies explored the effect of different pitches on the perceptions of agents. Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study. Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable and authoritative but less friendly \cite{jestin2022effects, tolmeijer2021female}\cmt{[81][62]}. For \citet{dubiel2020persuasive}\cmt{[60]}'s study, the agent with a lower mean pitch was selected as the more persuasive voice. This result may be demonstrating users' unconscious bias to select a male-sounding voice as more persuasive and authoritative over female-sounding voices that are commonly associated with higher pitches. While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices. Currently, there are no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}. There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.

Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive \cite{dubiel2020persuasive}\cmt{[60]}. This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques. In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likable, with a higher perceived social presence with the agent. These perceptions contribute to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests. In another study, \citet{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness. These persuasion techniques can be beneficial to help users achieve their goals, but they can also be used for harmful actions, such as trying to get users to believe in false information.

Another key area of concern is privacy. Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction. In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{dubiel2020persuasive, lee2020hear}\cmt{[60][23]}. This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}. Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.

>>>>

There has been some effort recently towards unifying the evaluation of conversational agents, such as the work by Finch et al. \cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols. More research is needed in this area to standardize the assessment of perceptions to make them consistent, granular, and comparable across literature. In the interim, we urge researchers to maintain the granularity of measurements to ensure that the subtleties among different perceptions of agents are preserved in their analysis.

@@

\subsection{Design Implications and Ethical Considerations}

Although there are existing research on the relationship between conversation architecture used by CAs and how users perceive them, there is currently a lack of a comprehensive understanding of these connections. Our work proposes a framework that establishes a foundational understanding of the current state of research and highlights under-explored areas that require further investigation. This framework also serves as a guide for designers by summarizing the various conversation architecture elements that can be utilized in design, along with their corresponding influences on user perception of agents. Designers can use this framework to understand how their choice of conversation architecture affects user perception of agents, or to design for specific perceptions of agents using conversation architecture elements. For instance, designers seeking to enhance the perception of competence in an agent may investigate the effects of initiative strategies, affective language, formal language, and different prosody settings. However, designers of conversational agents need to be aware of and consider ethical implications and potential negative impacts for users. There are three main areas of concern related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing users' actions, and privacy concerns.

For the element of prosody, various studies explored the effect of different pitches on the perceptions of agents. Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study. Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable and authoritative but less friendly \cite{jestin2022effects, tolmeijer2021female}\cmt{[81][62]}. For \citet{dubiel2020persuasive}\cmt{[60]}'s study, the agent with a lower mean pitch was selected as the more persuasive voice. This result may be demonstrating users' unconscious bias to select a male-sounding voice as more persuasive and authoritative over female-sounding voices that are commonly associated with higher pitches. While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices. Currently, there are no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}. There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}. To address the issue of gender stereotype, CA designers should give users easy access to choose from a variety of voices.

Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive \cite{dubiel2020persuasive}\cmt{[60]}. This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques. In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likable, with a higher perceived social presence with the agent. These perceptions contribute to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests. In another study, \citet{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness. These persuasion techniques can be beneficial to help users achieve their goals, but they can also be used for harmful actions, such as trying to get users to believe in false information. Designers who use persuasive techniques in CAs should be transparent about their goal of influencing human perceptions and behaviors, and ensure that their actions are in the best interest of the users.

Another key area of concern is privacy. Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction. In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{dubiel2020persuasive, lee2020hear}\cmt{[60][23]}. This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}. As such, CAs ought to be constructed in a manner that ensures complete clarity regarding the storage and usage of user data. Moreover, designers need to protect the privacy of users by taking into account the sensitivity of the data, determining who can access it, and devising measures to prevent malicious users from exploiting it.

\subsection{Limitations and Future Directions}

Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022. We may have missed literature published outside this time period, as well as in other libraries. Also, most of the studies in our corpus are based on lab experiments using short interactions with users. The generalizability of these findings needs to be verified through longer-term engagements with conversational agents deployed in real-world situations. 
Lastly, we needed to rely on our own interpretations to categorize some of the perception measures into the framework due to inconsistent protocols used in the evaluation of perceptions of agents.
%Lastly, research without empirical studies on the perception of agents is excluded based on our selection criteria. We may have missed some influential findings in these papers. %To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.

There are several future research directions that could enhance the proposed framework outlined in this paper. Firstly, establishing consistent measures for evaluating users' perceptions of agents is crucial to increase validity and consistency. Additionally, exploring under-examined aspects of the framework, such as how an agent's elaborateness affects its perceived ability (intelligence, competence, credibility), is necessary to further contribute to the body of knowledge. Moreover, delving deeper into the nuances that affect the relationship between conversation architecture and users' perceptions of agents is essential. This includes exploring contextual factors, such as users' prior experiences with conversational agents, as well as understanding how the combination of multiple conversation architecture elements can influence users' perceptions.

### 2023-06-06 sections/6-conclusion.tex
finalized copy uploaded to TAPS

In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs. Through our synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness). During our analysis, we found the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies. Further research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions. While our research contribute to the design conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.

>>>>

In this paper, we share our findings of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs. Through the synthesis of 57 papers in our corpus, we found that current literature has explored users' perceptions of agents related to interaction, ability, sociability and humanness in relation to the effects of conversation architecture (RQ1). Also, we observed that conversation architecture elements related to dialog strategy, content affectiveness, content style, and speech format are relevant to users' perceptions of agents (RQ2). Based on our in-depth analysis, we present a framework outlining the identified relationships between elements of agents' conversation architecture and aspects of users' perception (RQ3). Our investigation also revealed the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies. Also, more research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions. While our research contribute to the design of conversation architecture to orchestrate specific perceptions of agents, we urge designers to incorporate ethical perspectives into their design considerations, including potential gender stereotypes, the use of persuasive techniques to influence users, and privacy issues related to users disclosing sensitive information to agents.
